---
title: "The Cost of Repression: Bribery, Competence, and Informational Autocrats"
subtitle: |
  | University of Wisconsin-Milwaukee
  | Department of Political Science
mainfont: Trebuchet MS
author: "Kaan Aksoy"
date: "4th May 2022"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{siunitx}
  - \newcolumntype{d}{S[
      input-open-uncertainty = ,
      input-close-uncertainty = ,
      parse-numbers = false,
      table-align-text-pre = false,
      table-align-text-post = false
      ]}
output: 
  beamer_presentation:
    theme: "Dresden"
    latex_engine: xelatex
    fig_caption: yes
citation_package: biblatex
bibliography: presentationcitations.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
options("modelsummary_format_numeric_latex" = "plain")
```

```{r loading-libraries-and-data}
# Load packages
library(tidyverse)
library(RColorBrewer) # For colour-blind friendly palettes
library(estimatr)     # To cluster standard errors
library(modelsummary) # For neat reporting tables
library(kableExtra)   # For additional table formatting

# Load the data
df1 <- read_csv("~/GitHub/masterspaper/kaksoy_masterpaperdata.csv") %>% 
  mutate(., region = as_factor(region), # Doesn't import as factor, so this step is necessary.
         democracy = as_factor(democracy),
         marx = as_factor(marx),
         masskilling = as_factor(masskilling))

# Also need to recreate reversr
reversr <- function (x, na.rm = T) {
  min(x, na.rm = T) - x + max(x, na.rm = T)
}
```
# Introduction
## Background

- Authoritarian regimes are generally corrupt.

- Their levels of corruption, however, are not always the same.

- Why is this the case?

## Introduction

```{r, fig.height=5}
df_graphs %>% 
  filter(., year == 2010 & class == "Authoritarian") %>% 
  select(., c(v2x_libdem, v2x_corr, class, country_text_id)) %>% 
  ggplot(., aes(x = v2x_libdem,
                y = v2x_corr,
                colour = class)) +
  geom_point() +
  geom_hline(yintercept = mean(df_master$v2x_corr[df_master$class == "Authoritarian"],
                               na.rm = TRUE),
             linetype = "dashed") +
  geom_text_repel(aes(label = country_text_id),
                  max.overlaps = 4,
                  show.legend = FALSE) +
  annotate("text", x = 0.245, y = 0.715, label = "Mean corruption") +
  scale_colour_brewer(palette = "Dark2") +
  labs(title = "Corruption among authoritarian regimes",
       x = "Liberal Democracy Index",
       y = "Corruption Index",
       colour = "Regime type") +
  theme_classic() +
  theme(legend.position = "none")
```

## Research Question

- What accounts for the varying levels of corruption across authoritarian regimes?

## Hypotheses

Two hypotheses:

*H~1~*: Personalistic dictatorships will foster higher levels of executive corruption relative to party regimes.

*H~2~*: Regime duration is expected to have a higher effect on regime corruption in personalistic dictatorships compared to party regimes.

# Research Design and Data

## Research Design

Linear regression models to predict four different types of corruption.

- Executive bribery
- Executive theft
- Public sector bribery
- Public sector theft

## Variables

- Corruption type as dependent variable.

- Regime type is the independent variable: Party, or personalistic?

- Regime duration, natural resource rents, public sector impartiality as controls.

## Data

Data drawn from the Varieties of Democracy Project [@vdem2022] and @geddes_wright_frantz_2014. Data from the former available until 2022, but latter provides data only up until 2010; this is a limitation.

## Summary Statistics

```{r}
means <- sapply(df_master[df_master$class == "Authoritarian", c("v2regdur", "v2x_corr", "v2x_libdem", "v2excrptps_osp",
                     "v2exthftps_osp", "v2exbribe_osp", "v2exembez_osp", "v2clrspct_osp")],
                mean, na.rm = T)
sds <- sapply(df_master[df_master$class == "Authoritarian", c("v2regdur", "v2x_corr", "v2x_libdem", "v2excrptps_osp",
                     "v2exthftps_osp", "v2exbribe_osp", "v2exembez_osp", "v2clrspct_osp")],
                sd, na.rm = T)
mins <- sapply(df_master[df_master$class == "Authoritarian", c("v2regdur", "v2x_corr", "v2x_libdem", "v2excrptps_osp",
                     "v2exthftps_osp", "v2exbribe_osp", "v2exembez_osp", "v2clrspct_osp")],
                min, na.rm = T)
maxs <- sapply(df_master[df_master$class == "Authoritarian", c("v2regdur", "v2x_corr", "v2x_libdem", "v2excrptps_osp",
                     "v2exthftps_osp", "v2exbribe_osp", "v2exembez_osp", "v2clrspct_osp")],
                max, na.rm = T)
names <- c("Regime duration (days)", "Corruption Index",
           "Liberal Democracy Index", "Public sector bribery", "Public sector theft", "Executive bribery", "Executive theft", "Public administration impartiality")
table1 <- tibble("Variable" = names,
       "Mean" = means,
       "Standard Deviation" = sds,
       "Minimum" = mins,
       "Maximum" = maxs)

table1 %>%
  kbl(., digits = 3, format.args = list(big.mark = ","),
      caption = "Summary statistics for sample",
      format = "latex",
      booktabs = TRUE) %>%
  kable_classic_2(.) %>% 
  kable_styling(., bootstrap_options = "condensed",
                font_size = 6)
```

# Results

## Results

```{r}
fit1 <- lm(v2exbribe_osp ~ relevel(regimetype, ref = "3") +
             log(regimeduration) + v2clrspct_osp + log(e_total_resources_income_pc+0.0001),
           data = df_master)
fit2 <- lm(v2exembez_osp ~ relevel(regimetype, ref = "3") +
             log(regimeduration) + v2clrspct_osp + log(e_total_resources_income_pc+0.0001),
           data = df_master)
fit3 <- lm(v2excrptps_osp ~ relevel(regimetype, ref = "3") +
             log(regimeduration) + v2clrspct_osp + log(e_total_resources_income_pc+0.0001),
           data = df_master)
fit4 <- lm(v2exthftps_osp ~ relevel(regimetype, ref = "3") +
             log(regimeduration) + v2clrspct_osp + log(e_total_resources_income_pc+0.0001),
           data = df_master)

list1 <- list("Executive bribery" = fit1,
              "Executive theft" = fit2,
              "Public sector bribery" = fit3,
              "Public sector theft" = fit4)

modelsummary(list1,
             coef_map = c('relevel(regimetype, ref = "3")2' = "Regime: Party",
                          'relevel(regimetype, ref = "3")1' = "Regime: Personal",
                           'log(regimeduration)' = 'Logged regime duration',
                           'v2clrspct_osp' = 'Public administration impartiality',
                           'log(e_total_resources_income_pc + 1e-04)' = 'Logged natural resource rents',
                           '(Intercept)' = 'Intercept'),
             gof_omit = c('AIC|BIC|Log.Lik|RMSE'),
             stars = TRUE,
             title = 'Regime types and types of corruption',
             output = "kableExtra") %>%
  kable_classic_2(.) %>% 
  kable_styling(., bootstrap_options = "condensed",
                font_size = 5.5)
```

# Bibliography
## Bibliography

