---
title: "The Cost of Repression: Bribery, Competence, and Informational Autocrats"
subtitle: |
  | University of Wisconsin-Milwaukee
  | Department of Political Science
mainfont: Trebuchet MS
author: "Kaan Aksoy"
date: "4th May 2022"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{siunitx}
  - \newcolumntype{d}{S[
      input-open-uncertainty = ,
      input-close-uncertainty = ,
      parse-numbers = false,
      table-align-text-pre = false,
      table-align-text-post = false
      ]}
output: 
  beamer_presentation:
    theme: "Dresden"
    latex_engine: xelatex
    fig_caption: yes
citation_package: biblatex
bibliography: thesiscitations.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
options("modelsummary_format_numeric_latex" = "plain")
```

```{r loading-libraries-and-data}
# Load packages
library(tidyverse)
library(RColorBrewer) # For colour-blind friendly palettes
library(estimatr)     # To cluster standard errors
library(modelsummary) # For neat reporting tables
library(kableExtra)   # For additional table formatting

# Load the data.
df1 <- read_csv("~/GitHub/masterspaper/kaksoy_masterpaperdata.csv") %>% 
  mutate(., region = as_factor(region), # Doesn't import as factor, so this step is necessary.
         democracy = as_factor(democracy),
         marx = as_factor(marx),
         masskilling = as_factor(masskilling)) %>% 
  filter(., democracy == 0)

# Need to recreate reversr.
reversr <- function (x, na.rm = T) {
  min(x, na.rm = T) - x + max(x, na.rm = T)
}
```
# Research Question

- Modern autocracies use different methods to maintain power.

- The appearance of competence is a key component—how do they create this image?

- What is the relationship between the cost of repression and low-level bribery?

# Theory

- Informational autocracy [@guriev2019] leads to subtle means of repression, smart tactics to pre-empt dissent.

- Corruption unpacked: Bribery and embezzlement/theft as separate concepts.

- Petty bribery (e.g., traffic police, DMV clerk) impacts citizen perceptions severely.

- Autocrats who cannot repress will seek to decrease low-level bribery as a means of creating an image of competence.

# Hypotheses

- As cost of repression rises, low-level bribery will decrease.

- As regime legitimation on performance grounds rises, low-level bribery will decrease.

# Data and Design

- Primarily Varieties of Democracy [@vdem2023] data, some reinforcement with other data sets.

```{r descriptive-statistics}
datasummary((`Low-level bribery` = v2excrptps) +
              (`Physical violence index` = v2x_clphy) +
              (`Performance legitimation` = v2exl_legitperf) +
              (`Electoral democracy index` = v2x_polyarchy) +
              (`GDP per capita` = e_gdppc) +
              (`Time required to open business (days)` = businessdays) +
              (`Natural resource income as % of GDP` = naturalresourcerents) ~
              (Mean + SD + Max + Min + N), # Capital letters are important, these default na.rm = T
            data = df1,
            output = 'kableExtra') %>% 
  kable_styling(font_size = 6)
```

- Sample is formed from all autocracies, defined by their "electoral democracy index" score (less than 0.42).

- Unit of analysis is the country.

- Linear regressions, clustered standard errors to correct for autocorrelation between country-units.

# Findings

- Statistically significant relationship between political violence and low-level bribery.

- Less significant relationship between performance legitimation and low-level bribery.

- Null for H$_1$ rejected; null for H$_2$ is more difficult to reject. 

# Results and Tables
```{r models-1-4, fig.width=2, fig.height=2}
lm1 <- lm_robust(reversr(v2excrptps) ~ reversr(v2x_clphy),
                 subset = (democracy == 0),
                 data = df1,
                 clusters = country_text_id)
lm2 <- lm_robust(reversr(v2excrptps) ~ reversr(v2x_clphy) + v2exl_legitperf,
                 subset = (democracy == 0),
                 data = df1,
                 clusters = country_text_id)
lm3 <- lm_robust(reversr(v2excrptps) ~ reversr(v2x_clphy) + v2exl_legitperf +
                   log(e_gdppc),
                 subset = (democracy == 0),
                 data = df1,
                 clusters = country_text_id)
lm4 <- lm_robust(reversr(v2excrptps) ~ reversr(v2x_clphy) + v2exl_legitperf +
                   log(e_gdppc) + v2x_polyarchy,
                 subset = (democracy == 0),
                 data = df1,
                 clusters = country_text_id)

modelsummary(list(lm1, lm2, lm3, lm4),
             output = 'kableExtra',
             stars = c('*' = .1, '**' = .05, '***' = .01),
             coef_map = c('reversr(v2x_clphy)' = 'Physical violence index',
                          'v2exl_legitperf' = 'Performance legitimation',
                          'log(e_gdppc)' = 'Logged GDP per capita',
                          'v2x_polyarchy' = 'Electoral democracy index',
                          '(Intercept)' = 'Intercept'),
             gof_omit = 'BIC|Log.Lik.|RMSE|Std.Errors',
             notes = list('Standard errors clustered by country.'),
             title = "Basic Models") %>%
  add_header_above(c(" " = 1, "Low-level bribery" = 4)) %>% 
  kable_styling(font_size = 5)
```

# Bibliography

::: {#refs}
:::