---
title: "The Cost of Repression: Bribery, Competence, and Informational Autocrats"
subtitle: |
  | University of Wisconsin-Milwaukee
  | Department of Political Science
mainfont: Trebuchet MS
author: "Kaan Aksoy"
date: "4th May 2022"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{siunitx}
  - \newcolumntype{d}{S[
      input-open-uncertainty = ,
      input-close-uncertainty = ,
      parse-numbers = false,
      table-align-text-pre = false,
      table-align-text-post = false
      ]}
output: 
  beamer_presentation:
    theme: "Dresden"
    latex_engine: xelatex
    fig_caption: yes
citation_package: biblatex
bibliography: presentationcitations.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
options("modelsummary_format_numeric_latex" = "plain")
```

```{r loading-libraries-and-data}
# Load packages
library(tidyverse)
library(RColorBrewer) # For colour-blind friendly palettes
library(estimatr)     # To cluster standard errors
library(modelsummary) # For neat reporting tables
library(kableExtra)   # For additional table formatting

# Load the data
df1 <- read_csv("~/GitHub/masterspaper/kaksoy_masterpaperdata.csv") %>% 
  mutate(., region = as_factor(region), # Doesn't import as factor, so this step is necessary.
         democracy = as_factor(democracy),
         marx = as_factor(marx),
         masskilling = as_factor(masskilling))

# Also need to recreate reversr
reversr <- function (x, na.rm = T) {
  min(x, na.rm = T) - x + max(x, na.rm = T)
}
```
# Introduction
## Background

- Unpacking corruption into constituent parts

- Two dimensions: nature of corruption, and level of corruption

- Focusing on low-level bribery

- Relationship with "competence of government" aspect of informational autocracy

## Introduction

```{r, fig.height=5}

```

## Research Question

- What accounts for the varying levels of corruption across authoritarian regimes?

## Hypotheses

Two hypotheses:

*H~1~*: Personalistic dictatorships will foster higher levels of executive corruption relative to party regimes.

*H~2~*: Regime duration is expected to have a higher effect on regime corruption in personalistic dictatorships compared to party regimes.

# Research Design and Data

## Research Design

Linear regression models to predict four different types of corruption.

- Executive bribery
- Executive theft
- Public sector bribery
- Public sector theft

## Variables

- Corruption type as dependent variable.

- Regime type is the independent variable: Party, or personalistic?

- Regime duration, natural resource rents, public sector impartiality as controls.

## Data

Data drawn from the Varieties of Democracy Project [@vdem2022] and @geddes_wright_frantz_2014. Data from the former available until 2022, but latter provides data only up until 2010; this is a limitation.

## Summary Statistics

```{r}

```

# Results

## Results

```{r}

```

# Bibliography
## Bibliography

::: {#refs}
:::
